% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{JINXING WANG}

\basicInfo{
  \email{ustcstarJob@163.com} \textperiodcentered\ 
  \phone{(+86) 186-183-05535}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{University of Science and Technology of China (USTC)}, Hefei, China}{2006 -- 2010}
\textit{B.S.} in Statistics

\section{\faUsers\ Experience}
\datedsubsection{\textbf{JD Inc.} Beijing, China}{Nov. 2020 -- now}
Build up inverted index creation service.
\begin{itemize}
  \item Support modifying index config and showing the index content on web site. Use producer-consumer model to manage index's creation. Important index can be backed up and roll back.
  \item Support recall service and ABtest.
\end{itemize}
Build up forward index service.
\begin{itemize}
  \item Used brpc & jsf to build forward index service. Brpc is an industrial-grade RPC framework used through Baidu. Jsf is a high-performance service framework used through JingDong. The forward index service get and cache T+1 data from redis cluster, along with real-time data to form the protobuffer data and return.
  \item average time cost is 4ms, tp99 is 10ms.
\end{itemize}
Build up rank service.
\begin{itemize}
  \item Used brpc & jsf to build rank service. Rank service used user profile and goods profile to predict ctr score for each goods. Rank service used FM(Factorization Machines) model to predict ctr. FM model is a supervised algorithm that can be used for classification, regression, and ranking tasks. The rank service loaded FM model, deal with user profile and goods profile's discretization, and calculated the result.
  \item average time cost is 45ms, tp99 is 70ms.
\end{itemize}



\datedsubsection{\textbf{SOHU Inc.} Beijing, China}{Jan. 2018 -- Nov. 2020}
Refactor the recall-service from Java cache to Apache Thrift. The recall-service which makes use of collaborative filtering, content-based filtering etc is part of recommender systems and it mainly supplies candidate data to recommender systems. Recommender systems can be divided into recall-service(data supporter), rank-service(ctr estimation) and rerank-service(strategy).
\begin{itemize}
  \item Server: used TNonblockingServer to deal with client connections and service request. Used mmap to load data from disk to RAM. Designed special data structure to support inverted index and used protobuffer to support forward index.
  \item Client: used BasePooledObjectFactory to manage connection pool. Calculated the periodical fail rate of each serverNode and dispatched requests to the serverNodes whose fail rate was within the threshold. Test the bad serverNode(whose fail rate was beyond the threshold) background and reset the fail rate when the bad serverNode became normal.
  \item Test: used tcpdump and tcpcopy to test the recall-service before deployed to the product environment.
  \item Reduced recall-service's timeout(30ms) rate from 7.5‰ to 0.62‰.
\end{itemize}

Inverted index support filter rules. When dealing with inverted index, we sometimes need forward index to do some filtering. In this part, we add forward index's filtering result to the inverted index, so we can do forward index filtering while avoiding to query forward index. This helps to increase the query speed.
\begin{itemize}
  \item Index creation: used drools to mark the filter result in the inverted index.
  \item Server: added bitmap to inverted index's data structure
\end{itemize}

Make recall-service to have near real-time search.
\begin{itemize}
  \item Client: pushed new data gotten from Kafka to the server by thrift.
  \item Server: used Segment locking to manage the new data recieved from the client. Set a timeout on the new data and after the timeout had expired, the key would automatically be deleted.
  \item Cut down the recall-service index's update-time from 40 minutes to real-time.
\end{itemize}

Recall-service configure management and recall-service monitor.
\begin{itemize}
  \item Configure Management: used SpringBoot, MySQL, VUE to manage the configure.
  \item Monitor: used Grafana and InfluxDB to monitor request's QPS, latency etc.
\end{itemize}

\datedsubsection{\textbf{Renrenche Inc.} Beijing China}{July. 2015 -- Jan. 2018}
Evaluate pre-owned car's price
\begin{itemize}
  \item Used empirical model based on city, car model, used years to calculate pre-owned car's price.
  \item Designed and implemented data crawling, data cleaning and data training.
  \item Build up a website by using PHP CodeIgniter framework to make the evaluation as a product.
  \item The accuracy(The difference between real price and the evaluated price within 10\%) was 75.5\% and the bad case(the difference beyond 20\%) was 6.2\%.The result was as the same accuracy as Che300(A professional company focused on pre-owned car's price evaluation).
\end{itemize}

Support WeChat Pay
\begin{itemize}
  \item Used distributed locks with Redis to create an order.
  \item Used Symmetric-key algorithm to comunicate with WeChat Server
  \item Used RocketMQ to deal with the failure of notification of the WeChat Server
\end{itemize}

Refactor the insurance and loan modules from PHP CodeIgniter to Java SpringBoot.
\begin{itemize}
  \item Decoupled the insurance and loan modules from the main module to reduced the pressure of the key database.
  \item Used Kafka to get insurance clue from the dealed cars information and made the insurance fee and loan service fee can be paid through WeChat Pay.
\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Java > C++ > PHP > Python
  \item Databases: Redis > MySQL > Memcached
  \item Good at data structure and algorithm
\end{itemize}

\end{document}
